Cartograms with Dynamic Features

### 2022-03-02 paper/section/related.tex
draft: introduction

\new{Cartograms are representations of geographical space generated by the value-by-area mapping technique that combines statistical and geographical information. In this paper, we follow the categorization of cartograms by \citea{vankreveld2004Rectangular}: contiguous, non-contiguous, rectangular, and Dorling. While we focus on rectangular and Dorling cartograms in this paper, we provide brief definitions of contiguous and non-contiguous cartograms for interested readers: Contiguous cartograms are topology-preserving that maintain connectivity with their adjacent areas but have distortion in shape. Non-contiguous cartograms sacrifice the topological connectivity to enable growing or shrinking in size to maintain their original shape \cite{dent2009Cartography}.}

@@

\thumbnail{dorling}{
	Dorling cartograms are non-contiguous and do not preserve geography and topology. A Dorling cartogram is statistically accurate, regions are represented by circles and the data dimensions of interest are represented by the circle size \cite{dorling2011Area}. In a Demers cartogram, a variant of Dorling, squares are used instead to capture a certain level of topology \cite{cano2015Mosaic}. Dorling cartograms are unable to maintain topological accuracy as circles are often repositioned to remove overlap. \new{Here we focus on Demers cartograms as we use squares to depict regions. This style of cartogram offers the advantages that the comparisons between regions are more intuitive and the space utilization is more effcient.}
}

>>>>

\new{While we focus on rectangular and Dorling cartograms in this paper, we provide brief definitions of contiguous and non-contiguous cartograms for interested readers: Contiguous cartograms are topology-preserving that maintain connectivity with their adjacent areas but have distortion in shape. Non-contiguous cartograms sacrifice the topological connectivity to enable growing or shrinking in size to maintain their original shape \cite{dent2009Cartography}.}

@@

\thumbnail{dorling}{
	Dorling cartograms are non-contiguous and do not preserve geography and topology. A Dorling cartogram is statistically accurate, regions are represented by circles and the data dimensions of interest are represented by the circle size \cite{dorling2011Area}. In a Demers cartogram, a variant of Dorling, squares are used instead to capture a certain level of topology \cite{cano2015Mosaic}. Dorling cartograms are unable to maintain topological accuracy as circles are often repositioned to remove overlap. \new{Here we focus on Demers cartograms as we use squares to depict regions. This style of cartogram offers the advantages that the comparisons between regions are more intuitive and the space utilization is more effcient. Demers cartograms also have the advantage of preserving a higher level of topology. }
}
